Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-16 latex/tex/experiments.tex
levels section

From Figure \ref{fig:seqlevelbreakdown}, the MatMul cost decreases slightly per level, which

>>>>

From Figure \ref{fig:seqlevelbreakdown}, the MatMul cost decreases slightly per level, which may be explained by BLAS optimizations occurring in the
local matrix multiply, especially as each node's subproblem becomes smaller and smaller. The NNLS grows exponentially, which is exactly in line with theory,
and none of the levels seem to become bandwidth or latency bound for this case.

As we increase the nodes to 40 in the same sequential case, the story completely changes. Figure \ref{fig:parallellevelbreakdown} shows the MatMul cost is almost precisely the same, which is line with the theory.
The NNLS cost grows exponentially as before and becomes dominating at the lower levels. The latency is also appearing as the AllReduce cost, which is latency bound,
starts to grow exponentially from level 3 onwards.

In Figure \ref{fig:rwparallellevelbreakdown}, note that this levels experiment is from the image dataset, which is considerably larger than the synthetic case but is of the same size.
Although all is relatively the same as in Figure \ref{fig:parallellevelbreakdown}, matrix multiply still dominates at the lower levels and the problem is computationally bound
at each level, which is indiciative of the strong speedup as seen in the previous section.
